\begin{thebibliography}{99}


\bibitem{keith}
    Jeremy Keith:
    HTML5 for Web Designers, 2010


\bibitem{diveInto}
    Mark Pilgrim: 
    Dive into HTML5, 2010

\bibitem{vrml972}
    Rikk Carey, Gavin Bell:
    The Annotated VRML 97 Reference Manual, 1997


\bibitem{Shreiner}
    Dave Shreiner:
    OpenGL Programming Guide (Seventh Edition), 2009

\bibitem{beginnersGuide}
    Diego Cantor, Brandon Jones: 
    WebGL Beginner's Guide, 2012
    



\cleardoublepage
\hspace{-\leftmargin}{\Large\bfseries Web-Referenzen} % Wüster Hack %-|



\bibitem{KhronosAbout}
    Neil Trevett: Building Markets for Advanced Devices through Open Standards
    \url{http://www.khronos.org/assets/uploads/developers/library/overview/khronos_overview.pdf}, abgerufen am 18.08.2012.

\bibitem{SGI}
    SGI: OpenGL
    \url{http://www.sgi.com/products/software/opengl/?/overview.html}, abgerufen am 18.08.2012.

\bibitem{KhronosAbout2}
    About The Khronos Group
    \url{http://www.khronos.org/about}, abgerufen am 18.08.2012.

\bibitem{devGoogle}
    Android Developers: Andriod 2.2 APIs
    \url{http://developer.android.com/about/versions/android-2.2.html}, abgerufen am 18.08.2012.

\bibitem{devApple}
    OpenGL ES for iOS
    \url{https://developer.apple.com/devcenter/ios/resources/opengl-es/}, abgerufen am 18.08.2012.
    
\bibitem{operawebgl}
    Luz Caballero (Opera): An introduction to WebGL
    \url{http://dev.opera.com/articles/view/an-introduction-to-webgl/}, abgerufen am 18.08.2012.
        
\bibitem{webgl}
    Khronos Group: WebGL - OpenGL ES 2.0 for the Web
    \url{https://www.khronos.org/webgl/}, abgerufen am 18.08.2012.
    
\bibitem{W3Ccanvas}
    W3C: HTML5, The canvas element
    \url{http://www.w3.org/TR/html5/the-canvas-element.html#the-canvas-element}, abgerufen am 18.08.2012.

\bibitem{WHATWGcanvasContext}
    WHATWG: CanvasContexts
    \url{http://wiki.whatwg.org/wiki/CanvasContexts}, abgerufen am 18.08.2012.

\bibitem{WHATWGcanvas}
    WHATWG: The canvas element
    \url{http://www.whatwg.org/specs/web-apps/current-work/multipage/the-canvas-element.html}, abgerufen am 18.08.2012.

\bibitem{StatTop5Browser}
    StatCounter: Global Stats, Top 5 Browsers from Jun to Jul 2012
    \url{http://gs.statcounter.com/#browser-ww-monthly-201206-201207-bar}, abgerufen am 18.08.2012.

\bibitem{MSWebGL}
    Microsoft Security Research \& Defense: WebGL Considered Harmful
    \url{http://blogs.technet.com/b/srd/archive/2011/06/16/webgl-considered-harmful.aspx}, abgerufen am 18.08.2012.

\bibitem{Silverlight}
    Silverlight Blog: Silverlight 5 Available for Download Today
    \url{http://blogs.msdn.com/b/silverlight/archive/2011/12/09/silverlight-5-available-for-download-today.aspx}, abgerufen am 18.08.2012.

\bibitem{IEWebGL}
    IEWebGL: WebGL for Internet Explorer
    \url{http://iewebgl.com}, abgerufen am 18.08.2012.

\bibitem{MDNsop}
    Mozilla Developer Network: Same origin policy for JavaScript
    \url{https://developer.mozilla.org/en-US/docs/Same_origin_policy_for_JavaScript}, abgerufen am 18.08.2012.

\bibitem{cors}
    W3C: Cross-Origin Resource Sharing
    \url{http://www.w3.org/TR/cors/}, abgerufen am 18.08.2012.

\bibitem{iosopengl}
    OpenGL ES Programming Guide for iOS
    \url{http://developer.apple.com/library/ios/#documentation/3DDrawing/Conceptual/OpenGLES_ProgrammingGuide/Introduction/Introduction.html}, abgerufen am 19.08.2012.
    
\bibitem{sonywebgl}
    Sony Ericsson Dev: WebGL
    \url{https://github.com/sonyericssondev/WebGL}, abgerufen am 19.08.2012.
  
\bibitem{mobileos}
    StatCounter Global Stats: Top 8 Mobile Operating Systems from Jun to Jul 2012
    \url{http://gs.statcounter.com/#mobile_os-ww-monthly-201206-201207-bar}, abgerufen am 19.08.2012.

\bibitem{contextwebgl}
    James Forshaw: WebGL -- A New Dimension for Browser Exploitation
    \url{http://www.contextis.com/research/blog/webgl/}, abgerufen am 19.08.2012.
    
\bibitem{contextwebgl2}
    James Forshaw: WebGL -- More WebGL Security Flaws
    \url{http://www.contextis.com/research/blog/webgl/}, abgerufen am 19.08.2012.

\bibitem{corsbug}
    Benoit Jacob: Cross-domain WebGL textures disabled in Firefox 5
    \url{https://hacks.mozilla.org/2011/06/cross-domain-webgl-textures-disabled-in-firefox-5/}, abgerufen am 19.08.2012.

\bibitem{releaseChrome}
    Google Chrome Blog: A dash of speed, 3D and apps
    \url{http://chrome.blogspot.de/2011/02/dash-of-speed-3d-and-apps.html}, abgerufen am 19.08.2012.

\bibitem{releaseFirefox}
    Firefox 4 Release Notes
    \url{http://www.mozilla.org/en-US/firefox/4.0/releasenotes/}, abgerufen am 19.08.2012.

\bibitem{releaseSafari}
    WebGL Now Available in WebKit Nightlies
    \url{http://www.webkit.org/blog/603/webgl-now-available-in-webkit-nightlies/}, abgerufen am 19.08.2012.

\bibitem{releaseOpera}
    Opera 12.00 for Windows Changelog
    \url{http://www.opera.com/docs/changelogs/windows/1200/}, abgerufen am 19.08.2012.

\bibitem{statVersion}
    StatCounter Global Stats: Top 12 Browser Versions from Jun to Jul 2012
    \url{http://gs.statcounter.com/#browser_version-ww-monthly-201206-201207-bar}, abgerufen am 19.08.2012.

\bibitem{nox3d}
    W3C HTML5: Things that you can't do with this specification because they are better handled using other technologies that are further described herein
    \url{http://www.w3.org/TR/html5/no.html}, abgerufen am 20.08.2012.    
    
\bibitem{aboutw3c}
    W3C: Über das W3C
    \url{http://www.w3.org/TR/html5/no.html}, abgerufen am 21.08.2012.
    
\bibitem{w3cmembers}
    W3C: Current members
    \url{http://www.w3.org/Consortium/Member/List}, abgerufen am 21.08.2012.
    
\bibitem{mozdom}
    Mozilla Developer Network: What is the DOM?
    \url{https://developer.mozilla.org/en-US/docs/Gecko_DOM_Reference/Introduction}, abgerufen am 21.08.2012.
    
\bibitem{html5rocks} HTML5 Rocks: WebGL Fundamentals
    \url{http://www.html5rocks.com/en/tutorials/webgl/webgl_fundamentals/}, abgerufen am 20.8.2012

\bibitem{threejsdocs}
    THREE.js r50 Dokumentation
    \url{http://mrdoob.github.com/three.js/docs/50/}, abgerufen am 21.08.2012

\bibitem{x3dom}
    X3DOM: About
    \url{http://www.x3dom.org/?page_id=2}, abgerufen am 21.08.2012

\bibitem{x3domhtml}
    X3D and HTML5
    \url{http://www.web3d.org/x3d/wiki/index.php/X3D_and_HTML5}, abgerufen am 21.08.2012

\bibitem{vrml10}
    The Virtual Reality Modeling Language: Version 1.0 Specification
    \url{http://www.web3d.org/x3d/specifications/vrml/VRML1.0/}, abgerufen am 21.08.2012

\bibitem{vrml97}
    The Virtual Reality Modeling Language: International Standard ISO/IEC 14772-1:1997
    \url{http://www.web3d.org/x3d/specifications/vrml/ISO-IEC-14772-VRML97//}, abgerufen am 21.08.2012

\bibitem{2dcontext}
    W3C: HTML Canvas 2D Context
    \url{http://www.w3.org/TR/2dcontext/}, abgerufen am 21.08.2012

\bibitem{specGraph}
    Peter Kröner: HTML5 Spezifikations-Übersicht
    \url{https://github.com/SirPepe/SpecGraph}, abgerufen am 22.08.2012

\bibitem{w3cpr}
    W3C: W3C Confirms May 2011 for HTML5 Last Call, Targets 2014 for HTML5 Standard
    \url{http://www.w3.org/2011/02/htmlwg-pr.html }, abgerufen am 22.08.2012

\bibitem{vrml10}
    The Virtual Reality Modeling Language: Version 1.0 Specification
    \url{http://www.web3d.org/x3d/specifications/vrml/VRML1.0/}, abgerufen am 22.08.2012

\bibitem{vrml97}
    The Virtual Reality Modeling Language: International Standard ISO/IEC 14772-1:1997
    \url{http://www.web3d.org/x3d/specifications/vrml/ISO-IEC-14772-VRML97//}, abgerufen am 22.08.2012

\bibitem{2dcontext}
    W3C: HTML Canvas 2D Context
    \url{http://www.w3.org/TR/2dcontext/}, abgerufen am 22.08.2012







\end{thebibliography}


