\begin{thebibliography}{99}


\bibitem[Kei10]{keith}
    \textbf{HTML5 for Web Designers} \\
    \textit{Jeremy Keith} \\
    A Book Apart, 2010

\bibitem[Pil10]{diveInto}
    \textbf{Dive into HTML5}  \\
    \textit{Mark Pilgrim}, 2010 \\

\bibitem[CB97]{vrml972}
    \textbf{The Annotated VRML 97 Reference Manual} \\
    \textit{Rikk Carey, Gavin Bell} \\
    Addison-Wesley Professional, 1997


\bibitem[Shr09]{Shreiner}
    \textbf{OpenGL Programming Guide} (Seventh Edition) \\
    \textit{Dave Shreiner} \\
    Addison-Wesley Longman, 2009

\bibitem[CJ12]{beginnersGuide}
    \textbf{WebGL Beginner's Guide}  \\
    \textit{Diego Cantor, Brandon Jones} \\
    Packt Publishing, 2012
    
\bibitem[Isi12]{Isi12}
    \textbf{SumoViz, HTML5-based Visualization of Pedestrian Simulation Data} \\
    \textit{Mustafa K. Isik} \\
    TU München, 10. Mai 2012

\bibitem[ALS10]{ALS10}
    \textbf{CouchDB: The Definitive Guide} \\
    \textit{J. Chris Anderson, Jan Lehnardt, Noah Slater} \\
    O'Reilly, 2010
    
\bibitem[Hol11]{Hol11}
    \textbf{Writing and Querying MapReduce Views in CouchDB} \\
    \textit{Bradley Holt} \\
    O'Reilly, 2011
    
\bibitem[McL11]{McL11}
    \textbf{What Is Node?} \\
    \textit{Brett McLaughlin} \\
    O'Reilly, 2011
    
\bibitem[Fla06]{Fla06}
    \textbf{JavaScript: The Definitive Guide} \\
    \textit{David Flanagan} \\
    O'Reilly, 2006
    
    
\cleardoublepage
\hspace{-\leftmargin}{\Large\bfseries Web-Referenzen} % Wüster Hack %-|



\bibitem[Tre11]{KhronosAbout}
    Neil Trevett: Building Markets for Advanced Devices through Open Standards \\
    \url{http://www.khronos.org/assets/uploads/developers/library/overview/khronos_overview.pdf}, abgerufen am 18.08.2012.

\bibitem[SGI]{SGI}
    SGI: OpenGL \\
    \url{http://www.sgi.com/products/software/opengl/?/overview.html}, \\ abgerufen am 18.08.2012.

\bibitem[Khr]{KhronosAbout2}
    About The Khronos Group \\
    \url{http://www.khronos.org/about}, abgerufen am 18.08.2012.

\bibitem[Goo]{devGoogle}
    Android Developers: Andriod 2.2 APIs \\
    \url{http://developer.android.com/about/versions/android-2.2.html}, \\ abgerufen am 18.08.2012.

\bibitem[App]{devApple}
    OpenGL ES for iOS \\
    \url{https://developer.apple.com/devcenter/ios/resources/opengl-es/}, \\ abgerufen am 18.08.2012.
    
\bibitem[Cab]{operawebgl}
    Luz Caballero (Opera): An introduction to WebGL \\
    \url{http://dev.opera.com/articles/view/an-introduction-to-webgl/}, \\ abgerufen am 18.08.2012.
        
\bibitem[Ope]{webgl}
    Khronos Group: WebGL - OpenGL ES 2.0 for the Web \\
    \url{https://www.khronos.org/webgl/}, abgerufen am 18.08.2012.
    
\bibitem[W3c]{W3Ccanvas}
    W3C: HTML5, The canvas element \\
    \url{http://www.w3.org/TR/html5/the-canvas-element.html#the-canvas-element}, \\ abgerufen am 18.08.2012.

\bibitem[WHc]{WHATWGcanvasContext}
    WHATWG: CanvasContexts \\
    \url{http://wiki.whatwg.org/wiki/CanvasContexts}, abgerufen am 18.08.2012.

\bibitem[Whc2]{WHATWGcanvas}
    WHATWG: The canvas element \\
    \url{http://www.whatwg.org/specs/web-apps/current-work/multipage/the-canvas-element.html}, abgerufen am 18.08.2012.

\bibitem[Sta1]{StatTop5Browser}
    StatCounter: Global Stats, Top 5 Browsers from Jun to Jul 2012 \\
    \url{http://gs.statcounter.com/#browser-ww-monthly-201206-201207-bar},  \\abgerufen am 18.08.2012.

\bibitem[MSFT]{MSWebGL}
    Microsoft Security Research \& Defense: WebGL Considered Harmful \\
    \url{http://blogs.technet.com/b/srd/archive/2011/06/16/webgl-considered-harmful.aspx}, abgerufen am 18.08.2012.

\bibitem[Sil]{Silverlight}
    Silverlight Blog: Silverlight 5 Available for Download Today \\
    \url{http://blogs.msdn.com/b/silverlight/archive/2011/12/09/silverlight-5-available-for-download-today.aspx}, abgerufen am 18.08.2012.

\bibitem[IEWeb]{IEWebGL}
    IEWebGL: WebGL for Internet Explorer \\
    \url{http://iewebgl.com}, abgerufen am 18.08.2012.

\bibitem[MDN]{MDNsop}
    Mozilla Developer Network: Same origin policy for JavaScript \\
    \url{https://developer.mozilla.org/en-US/docs/Same_origin_policy_for_JavaScript}, abgerufen am 18.08.2012.

\bibitem[W3cors]{cors}
    W3C: Cross-Origin Resource Sharing \\
    \url{http://www.w3.org/TR/cors/}, abgerufen am 18.08.2012.

\bibitem[AoGL]{iosopengl}
    OpenGL ES Programming Guide for iOS \\
    \url{http://developer.apple.com/library/ios/#documentation/3DDrawing/Conceptual/OpenGLES_ProgrammingGuide/Introduction/Introduction.html}, abgerufen am 19.08.2012.
    
\bibitem[SNE]{sonywebgl}
    Sony Ericsson Dev: WebGL \\
    \url{https://github.com/sonyericssondev/WebGL}, \\ abgerufen am 19.08.2012.
  
\bibitem[Sta2]{mobileos}
    StatCounter Global Stats: Top 8 Mobile Operating Systems from Jun to Jul 2012 \\
    \url{http://gs.statcounter.com/#mobile_os-ww-monthly-201206-201207-bar}, \\ abgerufen am 19.08.2012.

\bibitem[Con1]{contextwebgl}
    James Forshaw: WebGL -- A New Dimension for Browser Exploitation \\
    \url{http://www.contextis.com/research/blog/webgl/}, abgerufen am 19.08.2012.
    
\bibitem[Con2]{contextwebgl2}
    James Forshaw: WebGL -- More WebGL Security Flaws \\
    \url{http://www.contextis.com/research/blog/webgl/}, abgerufen am 19.08.2012.

\bibitem[Moz]{corsbug}
    Benoit Jacob: Cross-domain WebGL textures disabled in Firefox 5 \\
    \url{http://tinyurl.com/hacks-mozilla}, abgerufen am 19.08.2012.

\bibitem[Chr]{releaseChrome}
    Google Chrome Blog: A dash of speed, 3D and apps \\
    \url{http://chrome.blogspot.de/2011/02/dash-of-speed-3d-and-apps.html},  \\ abgerufen am 19.08.2012.

\bibitem[FF4]{releaseFirefox}
    Firefox 4 Release Notes \\
    \url{http://www.mozilla.org/en-US/firefox/4.0/releasenotes/}, \\ abgerufen am 19.08.2012.

\bibitem[Saf]{releaseSafari}
    WebGL Now Available in WebKit Nightlies \\
    \url{http://www.webkit.org/blog/603/webgl-now-available-in-webkit-nightlies/}, abgerufen am 19.08.2012.

\bibitem[Ope]{releaseOpera}
    Opera 12.00 for Windows Changelog \\
    \url{http://www.opera.com/docs/changelogs/windows/1200/}, abgerufen am 19.08.2012.

\bibitem[Sta3]{statVersion}
    StatCounter Global Stats: Top 12 Browser Versions from Jun to Jul 2012 \\
    \url{http://gs.statcounter.com/#browser_version-ww-monthly-201206-201207-bar}, abgerufen am 19.08.2012.

\bibitem[W3no]{nox3d}
    W3C HTML5: Things that you can't do with this specification because they are better handled using other technologies that are further described herein \\
    \url{http://www.w3.org/TR/html5/no.html}, abgerufen am 20.08.2012.    
    
\bibitem[W3a]{aboutw3c}
    W3C: Über das W3C \\
    \url{http://www.w3.org/TR/html5/no.html}, abgerufen am 21.08.2012.
    
\bibitem[W3m]{w3cmembers}
    W3C: Current members \\
    \url{http://www.w3.org/Consortium/Member/List}, abgerufen am 21.08.2012.
    
\bibitem[MDN1]{mozdom}
    Mozilla Developer Network: What is the DOM? \\
    \url{https://developer.mozilla.org/en-US/docs/Gecko_DOM_Reference/Introduction}, abgerufen am 21.08.2012.
    
\bibitem[HTML]{html5rocks} HTML5 Rocks: WebGL Fundamentals \\
    \url{http://www.html5rocks.com/en/tutorials/webgl/webgl_fundamentals/}, \\ abgerufen am 20.8.2012

\bibitem[THREE]{threejsdocs}
    THREE.js r50 Dokumentation \\
    \url{http://mrdoob.github.com/three.js/docs/50/}, abgerufen am 21.08.2012

\bibitem[X3D]{x3dom}
    X3DOM: About \\
    \url{http://www.x3dom.org/?page_id=2}, abgerufen am 21.08.2012

\bibitem[Web3]{x3domhtml}
    X3D and HTML5 \\
    \url{http://www.web3d.org/x3d/wiki/index.php/X3D_and_HTML5}, \\ abgerufen am 21.08.2012

\bibitem[VRML1]{vrml10}
    The Virtual Reality Modeling Language: Version 1.0 Specification \\
    \url{http://www.web3d.org/x3d/specifications/vrml/VRML1.0/}, \\ abgerufen am 21.08.2012

\bibitem[VRML97]{vrml97}
    The Virtual Reality Modeling Language: International Standard  \\
    \url{http://www.web3d.org/x3d/specifications/vrml/ISO-IEC-14772-VRML97//}, \\ abgerufen am 21.08.2012

\bibitem[2Dc]{2dcontext}
    W3C: HTML Canvas 2D Context \\
    \url{http://www.w3.org/TR/2dcontext/}, abgerufen am 21.08.2012

\bibitem[spec]{specGraph}
    Peter Kröner: HTML5 Spezifikations-Übersicht \\
    \url{https://github.com/SirPepe/SpecGraph}, abgerufen am 22.08.2012

\bibitem[W3l]{w3cpr}
    W3C: W3C Confirms May 2011 for HTML5 Last Call \\
    \url{http://www.w3.org/2011/02/htmlwg-pr.html }, abgerufen am 22.08.2012

\bibitem[VRML1a]{vrml10}
    The Virtual Reality Modeling Language: Version 1.0 Specification \\
    \url{http://www.web3d.org/x3d/specifications/vrml/VRML1.0/}, \\ abgerufen am 22.08.2012

\bibitem[VRMLa]{vrml97}
    The Virtual Reality Modeling Language: International Standard \\
    \url{http://www.web3d.org/x3d/specifications/vrml/ISO-IEC-14772-VRML97//},  \\ abgerufen am 22.08.2012

\bibitem[W32d]{2dcontext}
    W3C: HTML Canvas 2D Context \\
    \url{http://www.w3.org/TR/2dcontext/}, abgerufen am 22.08.2012

\bibitem[Win]{windows}
    Microsoft: Timeout Detection and Recovery of GPUs \\
    \url{http://msdn.microsoft.com/en-us/windows/hardware/gg487368.aspx}, \\ abgerufen am 28.08.2012

\bibitem[KhrSec]{KhrSec}
    Khronos Group: WebGL Security \\
    \url{http://msdn.microsoft.com/en-us/windows/hardware/gg487368.aspx}, \\ abgerufen am 28.08.2012

\bibitem[SPON1]{spon1}
    Spiegel Online: Warum die Wege des Menschen unberechenbar sind \\
    \url{http://spon.de/ac51E}, abgerufen am 01.09.2012

\bibitem[SPON2]{spon2}
    Spiegel Online: Der kürzeste Weg ist das Ziel \\
    \url{http://spon.de/adlhZ}, abgerufen am 01.09.2012

\bibitem[jQu]{jQu}
    jQuery UI \\
    \url{http://jqueryui.com/home}, abgerufen am 03.09.2012

\bibitem[MrD]{MrD}
    THREE.js Stats - JavaScript Performance Monitor \\
    \url{https://github.com/mrdoob/stats.js}, abgerufen am 01.09.2012
    
\bibitem[COL]{COL}
    COLLADA Digital Asset and FX Exchange Schema \\
    \url{https://collada.org/mediawiki/index.php/COLLADA_-_Digital_Asset_and_FX_Exchange_Schema}, abgerufen am 05.09.2012

\bibitem[W3s]{W3s}
    W3C: WebStorage \\
    \url{http://www.w3.org/TR/webstorage/}, abgerufen am 06.09.2012
    
\bibitem[Res12]{Res12}
    John Resig: How JavaScript Timers Work \\
    \url{http://ejohn.org/blog/how-javascript-timers-work/}, abgerufen am 06.09.2012
    
\bibitem[Iri11]{Iri11}
    Paul Irish: requestAnimationFrame for smart animating \\
    \url{http://paulirish.com/2011/requestanimationframe-for-smart-animating/}, \\ abgerufen am 07.09.2012
    
\bibitem[Gub09]{Gub09}
    Martin Gubisch: Kugelkoordinaten \\
    \url{http://www.martingubisch.de/cms/upload/files/tutorien/09\%20Kugelkoordinaten.pdf}, abgerufen am 07.09.2012
        
\bibitem[MSDN]{MSDN}
    Microsoft: Billboarding \\ 
    \url{http://msdn.microsoft.com/de-de/library/bb172358(VS.85).aspx}, \\ abgerufen am 07.09.2012

\bibitem[vdB00]{vdB00}
    John van der Burg: Building an Advanced Particle System \\
    \url{http://www.gamasutra.com/view/feature/3157/building_an_advanced_particle_.php}, abgerufen am 07.09.2012
    
\bibitem[Wie]{Wie}
    Lyle Wiedeman: Information on the HSV color space \\
    \url{http://dcssrv1.oit.uci.edu/~wiedeman/cspace/me/infohsv.html}, \\ abgerufen am 07.09.2012
    
\end{thebibliography}


